---
title: "product_by_brand"
Author: "Anh Hoang"
Date: "April 16th, 2022"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Libraries
```{r libraries}
library(readxl)
library(tidyverse)
library(caret)
library(dplyr)
library(stringr)
library(knitr)
library(treemap)
library(rio)
library(lubridate)
library(reshape2)
```
Data Imports
```{r import, include=FALSE}
Summary_Basket_2019 <- read_csv("Summary_Basket_2019.csv")
#Summary_Basket_2020 <- read_csv("Summary_Basket_2020.csv")
#Summary_Basket_2021 <- read_csv("Summary_Basket_2021.csv")
#UPC_Hack_Cereal2 <- read_csv("UPC_Hack_Cereal2.csv")
#UPC_Hack_Cleaners2 <- read_csv("UPC_Hack_Cleaners2.csv")
#Hackathon_Data_Maps <- read_excel("Hackathon_Data_Maps.xlsx")
```
Convert number to %
```{r convert_to_percent}
percent <- function(x, digits = 2, format = "f", ...) {
	paste0(formatC(x * 100, format = format, digits = digits, ...), "%")}
```

** Analysis
```{r Online_vs_Offline_byUPC_Hack_Cereal2_}
tmp <- UPC_Hack_Cereal2 %>% 
     group_by(Online) %>% 
     summarize(count = n()) %>%
     arrange(desc(count)) %>%
     mutate(Online = as.factor(Online)) %>%
     mutate(propotion = count/sum(count))
kable(tmp)
tmp %>% 
     ggplot(aes(x=Online,y=propotion,fill=Online))+
     geom_text(aes(label=percent(propotion)), vjust=-0.2)+
     geom_bar(stat="identity")
```

* Majority prefer to buy cereal in store (~93%)

```{r top_Cereal_Brand_byUPC_Hack_Cereal2_}
names(Hackathon_Data_Maps)[names(Hackathon_Data_Maps) == "UPC"] <- "upc"
names(Hackathon_Data_Maps)[names(Hackathon_Data_Maps) == "Parent Brand"] <- "Parent_Brand"
tmp2 <- UPC_Hack_Cereal2 %>% 
	group_by(upc) %>% 
	summarize(total = sum(qty)) %>% 
	#top_n(30, wt = total) %>%
	mutate(propotion = total/sum(total)) %>%
	left_join(Hackathon_Data_Maps, by="upc") %>%
	select("upc", "total", "propotion", "Parent_Brand", "Brand") %>%
	group_by(Parent_Brand, Brand) %>%
  arrange(desc(total)) 
kable(tmp2)

treemap(tmp2,index=c("Parent_Brand","Brand"),vSize="total",title="",palette="Set3",border.col="#FFFFFF")

tmp2 %>%
  ggplot(aes(x=reorder(Parent_Brand,-propotion), y=propotion))+
  geom_bar(stat="identity",fill="red")+
  theme(axis.text.x=element_text(angle=90, hjust=1),axis.title.x = element_blank())

head(tmp2, 50) %>%
  ggplot(aes(x=reorder(Brand,-propotion), y=propotion))+
  geom_bar(stat="identity",fill="red")+
  theme(axis.text.x=element_text(angle=90, hjust=1),axis.title.x = element_blank())
```

* Analyze top products in Cereal (2019-2021)
Top parent brands: Big G, Kelloggs. Counted for a total of ~70% cereal in stores
Most favorite brand: Cheerios (>15%)

```{r Online_byCerealBrand}
tmpOnline <- UPC_Hack_Cereal2 %>%
     group_by(upc, Online) %>%
     summarize(count=n()) %>% 
     filter(Online == 1) %>%
     arrange(desc(count)) %>%
     left_join(Hackathon_Data_Maps, by="upc") %>%
     select("upc", "count", "Parent_Brand", "Brand") %>%
     group_by(Parent_Brand, Brand)
kable(tmpOnline)

tmpOnline %>%
  ggplot(aes(x=reorder(Parent_Brand,-count), y=count))+
  geom_bar(stat="identity",fill="blue")+
  theme(axis.text.x=element_text(angle=90, hjust=1),axis.title.x = element_blank())

```
* BigG and Kelloggs also take major leads in online order


```{r top_Cereal_Brand_byUPC_Hack_Cleaner_}
Data_Maps2 <- import_list("Hackathon_Data_Maps.xlsx")

names(Data_Maps2$`Cleaners UPCs`)[names(Data_Maps2$`Cleaners UPCs`) == "UPC"] <- "upc"
names(Data_Maps2$`Cleaners UPCs`)[names(Data_Maps2$`Cleaners UPCs`) == "Parent Brand"] <- "Parent_Brand"


tmpClean <- UPC_Hack_Cleaners2 %>% 
	group_by(upc) %>% 
	summarize(total = sum(qty)) %>% 
	#top_n(30, wt = total) %>%
	mutate(propotion = total/sum(total)) %>%
	left_join(Data_Maps2$`Cleaners UPCs`, by="upc") %>%
	select("upc", "total", "propotion", "Parent_Brand", "Brand") %>%
  na.omit() %>%
	group_by(Parent_Brand, Brand) %>%
  arrange(desc(total)) 

kable(tmpClean)

treemap(tmpClean,index=c("Parent_Brand","Brand"),vSize="total",title="",palette="Set3",border.col="#FFFFFF")

tmpClean %>%
  ggplot(aes(x=Parent_Brand, y=propotion))+
  geom_bar(stat="identity",fill="red")+
  theme(axis.text.x=element_text(angle=90, hjust=1),axis.title.x = element_blank())

head(tmpClean, 50) %>%
  ggplot(aes(x=Brand, y=propotion))+
  geom_bar(stat="identity",fill="red")+
  theme(axis.text.x=element_text(angle=90, hjust=1),axis.title.x = element_blank())
```


```{r test - DONT' RUN}
#combine dataset in 20,21,22
Summary_Basket_1921 <- rbind(Summary_Basket_2019, Summary_Basket_2020, Summary_Basket_2021)
#Check for NA value - No NA existed
sum(is.na(Summary_Basket_1921))
#Convert date
Summary_Basket_1921$date <- as.Date(as.character(Summary_Basket_1921$date), format ='%y-%m-%d')
Summary_Basket_1921$year <- year(Summary_Basket_1921$date)
Summary_Basket_1921$month <- month(Summary_Basket_1921$date)
Summary_Basket_1921$day <- day(Summary_Basket_1921$date)
Summary_Basket_1921$weekday <- weekdays(Summary_Basket_1921$date)
#Overview on Basket 19-21
summary(Summary_Basket_1921)

```
** Over 3 years 19-21, each household spend an average of $31.40 and around 14 items/purchase. The amount of online purchase is quite small (0.01 mean).   


```{r test2}
#Check for NA value - No NA existed
sum(is.na(Summary_Basket_2019))
#Convert date
Summary_Basket_2019$date <- as.Date(as.character(Summary_Basket_2019$date), format='%y-%m-%d')
Summary_Basket_2019$year <- year(Summary_Basket_2019$date)
Summary_Basket_2019$month <- month(Summary_Basket_2019$date)
Summary_Basket_2019$day <- day(Summary_Basket_2019$date)
Summary_Basket_2019$weekday <- weekdays(Summary_Basket_2019$date)
#Overview on Basket 19-21
summary(Summary_Basket_2019)
#Check to see missing data
colSums(is.na(Summary_Basket_2019))
is.null(Summary_Basket_2019)
#Check numeric columns to subset
sapply(Summary_Basket_2019, is.numeric)
Summary_Basket_2019_numcols <- select(Summary_Basket_2019, "HHID", "Store", "totqty", "totdol", "Online")
#Find correlation
cor(Summary_Basket_2019_numcols)
melted_corr <- melt(cor(Summary_Basket_2019_numcols))
ggplot(data = melted_corr, aes(x = Var1, y = Var2, fill = value)) 
+ geom_tile() + scale_fill_gradient(low="grey", high="darkred") 
+ geom_text(aes(x = Var1, y = Var2, label =round(value, 2)), size = 4) 
+ labs(title = "Correlation Matrix", fill = "Coefficient Range") 
+ theme(axis.text.x=element_text(angle=45, vjust = 0.5))

#Analyze by store
Summary_Basket_2019 %>% select(Store) %>% distinct() %>% count()
#aggregate(Summary_Basket_2019$totdol~Summary_Basket_2019$Store, data = Summary_Basket_2019, sum)
most_popular_shop <- Summary_Basket_2019 %>% group_by(Store) %>% summarise(total.sales = sum(totdol)) %>% arrange(desc(total.sales)) %>% ungroup() %>% top_n(20, total.sales)
shopRevenue2019 <- ggplot(data = most_popular_shop, aes(x=reorder(as.factor(Store), total.sales), y = total.sales, fill = as.factor(Store))) + geom_bar(stat = "identity", show.legend = FALSE) + coord_flip() + labs(title = "Most popular store with most sales", x = "Store", y = "Total Sales", fill = "Store") 

shop_vs_hhid <- Summary_Basket_2019 %>% group_by(Store) %>% summarise(total.hhid = n_distinct(HHID)) %>% arrange(desc(total.hhid)) %>% ungroup() %>% top_n(20, total.hhid)
shopHouseHold2019 <- ggplot(data = shop_vs_hhid, aes(x=reorder(as.factor(Store), total.hhid), y = total.hhid, fill = as.factor(Store))) + geom_bar(stat = "identity", show.legend = FALSE) + coord_flip() + labs(title = "Store with most households coming", x = "Store", y = "Total Household", fill = "Store") 

require(gridExtra)
grid.arrange(shopHouseHold2019, shopRevenue2019, ncol = 2)

```
** 
There are a total of 51 stores and 363,785 households available in this analysis.
In 2019, these 51 stores sold ~182M items, generating $643M revenue.
Household tends to purchase around $45/purchase and 12-13 items/purchase.
Store 15 and 7 generate most revenue, with ~40M revenue in 2019.
However, store with most households coming are store 21 and 27, attracting ~60k households stopping by. However, their revenue are just around top 10. 
On the other hand, store 7 attracts less than >10k customers but still generate >$10M compared to store 21 in 2019.  
What makes this differences? Are these two located in lower income area, or the high products offered not enough? We need further analysis on this. 
On further analysis to see relationship between household and sales. 



