---
title: "Shopper_Investigation"
author: "Jonah Schnettler"
date: "April 15, 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Imports and Libraries

##Libraries
```{r libraries}
#install.packages("ggpubr")
library(readxl)
library(tidyverse)
library(ggpubr)
library(caret)
library(dplyr)
library(stringr)
```
*inlude librarys here. Commented section is example code for installing any missing packages.

##Data Imports
```{r import, include=FALSE}
Shopper_Tabs1 <- read_excel("Shopper_Tabs_1.xlsx")
Shopper_Tabs2 <- read_excel("Shopping_Tabs_2.xlsx")
Shopper_Tabs3 <- read_excel("Shopper_Tabs_3.xlsx")
```
*Import the data sets for shopper_tabs. Refactoring names is necessary for this.

#Clean/build workable data.

## Remove empty rows.
```{r remove_empty_rows}
remove_empty_rows <- function(.source) {
  empty_rows <- apply(.source, 1, function(.source) all(is.na(.source))) # Check each row for any rows that contain only na's.
  cleaned <- .source[!empty_rows,] # Keep everything but the empty rows.
  cleaned <- subset(cleaned, select = -c(2)) # Remove the percentage down column.
  return(cleaned)
}
```
*First step is to clear the empty rows after initial imports and then remove the percentage down column since it is constant for all data.

##Look at a specific set of data.
```{r get_data}
get_data <- function(.data, key) {
  found <- FALSE
  key_pattern <- paste("Demographic.*", key) # Look for row containing 'Demographic' followed by the key string we are looking for
  for(i in 1:nrow(.data)) { 
    if (grepl(pattern=key_pattern, .data [i, 1])) { # Check if current row has key_pattern matched.
      found <- TRUE # Set key pattern found and look for the end of this chunk.
      j <- i+1 # Set begginning position of this chunk.
      i <- i+1 # Skip next check since pattern found at this row.
    }
    if (grepl(pattern="Demographic.*", .data[i, 1]) && found) { # Check for next occurance of 'Demographic'
      new_data <- .data[j:i-1, 1:ncol(.data)] # Create subset of data that only contains a single table from the original excel.
      found <- FALSE
    }
  }
  if (found) { # If key pattern found and no other occurance of 'Demographic' set i to end of .data
    j <- j-1
    new_data <- .data[j:nrow(.data), 1:ncol(.data)] # Create subset of data that only contains a single table from the original excel.
    found <- FALSE
  } 
  if (!exists("new_data")) {
    for (a in 1:nrow(.data)) {
      if (grepl(pattern="Demographic.*", .data[a, 1])) { # Check for next occurance of 'Demographic'
        new_data <- .data[1:a-1, 1:ncol(.data)] # Create subset of data that only contains a single table from the original excel.
        break
      }
    }
    names(new_data)[2] <- new_data[1,2]
    names(new_data)[3:ncol(new_data)] <- new_data[2, 3:ncol(new_data)]
    new_data <- new_data[3:nrow(new_data),]
  } else {
    names(new_data)[1] <- new_data[1,1]
    names(new_data)[2] <- new_data[2,2]
    names(new_data)[3:ncol(new_data)] <- new_data[3, 3:ncol(new_data)]
    new_data <- new_data[4:nrow(new_data),]
  }
  new_data <- new_data[-c(3), ]
  return(new_data)
}
```
*Now we can look at the specific table by specifying a keyword to find said table. If failed, returns first table found in data passed; to overcome, give more specific key term for table.

##get weighted and unweighted data.
```{r get_weighted}
get_weighted <- function(.data, weight) {
  weighted_df <- as.data.frame(.data)
  for (i in 3:nrow(.data)) {
    weighted_df[i,1] <- as.data.frame(.data[i,1])
    for (j in 2:ncol(.data)) {
      weighted_df[1, j] <- as.data.frame(.data[1,j])
      weighted_df[i, j] <- round(as.numeric(weighted_df[i, j]) %*% as.numeric(weighted_df[weight, j]), 0)
    }
  }
  weighted_df <- weighted_df[-c(1,2),]
  names(weighted_df)[1] <- "question"
  return(weighted_df)
}
```
*This function calculates the weighted and unweighted data. To select weight, pass integer of 1 for unweighted and 2 for weighted.

## Pivot data.
```{r pivot}
pivot_data <- function(.data) {
  .data <- .data %>%
  pivot_longer(c('Male','Female','Other'), names_to = "Gender", values_to = "gender_amount") %>%
  pivot_longer(c('Age - 15-19','Age - 20-29','Age - 30-39','Age - 40-49','Age - 50-59','Age - 60+'), names_to = "ages", values_to = "ages_amount") %>%
  pivot_longer(c('Household Income - Low','Household Income - Medium-Low','Household Income - Medium-High','Household Income - High'), names_to = "incomes", values_to = "incomes_amount") %>%
  pivot_longer(c('Education - High School Grad or Less','Education - College/Post-Grad'), names_to = "education", values_to = "education_amount") %>%
  pivot_longer(c('Kids in Hhld Age 0-8','Kids in Hhld Age 9-19'), names_to = "kids", values_to = "kids_amount") %>%
  pivot_longer(c('Employed - Not Employed','Employed - Employed Part-Time','Employed - Employed Full-Time'), names_to = "employed", values_to = "employed_amount") %>%
  pivot_longer(c('Legal Drinking Age'), names_to = "alcoholic", values_to = "alcoholic_amount") %>%
  pivot_longer(c('White','Black or African American','Asian','Native American/American Indian','Mixed race/ Multiracial','Other (TYPE IN RESPONSE)','Prefer not to answer / No answer'), names_to = "ethnicity", values_to = "ethnicity_amount") %>%
  pivot_longer(c('Yes, of Spanish/Hispanic/Latino origin','No'), names_to = "hispanic", values_to = "hispanic_amount")
  return(.data)
}
```
*This function pivots all of the columns to be grouped.

## Start here!
```{r initialize data}
#Clean excel imported data
Shopper_Tabs1 <- remove_empty_rows(Shopper_Tabs1)
Shopper_Tabs2 <- remove_empty_rows(Shopper_Tabs2)
Shopper_Tabs3 <- remove_empty_rows(Shopper_Tabs3)

# This section generates the individual tables for shopper_tabs1
s1_past_six_months <- get_data(Shopper_Tabs1, "past 6 months")
s1_mobile_devices <- get_data(Shopper_Tabs1, "Smartphones")
s1_household_washing <- get_data(Shopper_Tabs1, "Household washing")
s1_haircare <- get_data(Shopper_Tabs1, "Haircare")
s1_skincare <- get_data(Shopper_Tabs1, "Skincare")
s1_cosmetics <- get_data(Shopper_Tabs1, "Make-up, cosmetics")
s1_packaged_food <- get_data(Shopper_Tabs1, "Packaged food")
s1_toys <- get_data(Shopper_Tabs1, "Toys")
s1_small_home_appliances <- get_data(Shopper_Tabs1, "Small home appliances")
s1_fashion <- get_data(Shopper_Tabs1, "Clothing/fashion")
s1_healthcare <- get_data(Shopper_Tabs1, "OTC healthcare")
s1_major_home_appliances <- get_data(Shopper_Tabs1, "Major home appliances")
s1_replacement_auto <- get_data(Shopper_Tabs1, "Replacement auto")
s1_streaming <- get_data(Shopper_Tabs1, "Streaming")
s1_wearables <- get_data(Shopper_Tabs1, "Wearables")
s1_computing <- get_data(Shopper_Tabs1, "Computing")
s1_home_furnishings <- get_data(Shopper_Tabs1, "furnishings")

# This section generates the individual tables for shopper_tabs2
s2_smartphones <- get_data(Shopper_Tabs2, "Smartphones")
s2_household_washing <- get_data(Shopper_Tabs2, "Household washing")
s2_haircare <- get_data(Shopper_Tabs2, "Haircare")
s2_skincare <- get_data(Shopper_Tabs2, "Skincare")
s2_cosmetics <- get_data(Shopper_Tabs2, "Make-up")
s2_packaged_food <- get_data(Shopper_Tabs2, "Packaged food")
s2_toys <- get_data(Shopper_Tabs2, "Toys")
s2_small_home_appliances <- get_data(Shopper_Tabs2, "Small home appliances")
s2_fashion <- get_data(Shopper_Tabs2, "Clothing")
s2_major_home_appliances <- get_data(Shopper_Tabs2, "Major home appliances")
s2_replacement_auto <- get_data(Shopper_Tabs2, "Replacement auto")
s2_streaming <- get_data(Shopper_Tabs2, "Streaming")
s2_wearables <- get_data(Shopper_Tabs2, "Wearables")
s2_computing <- get_data(Shopper_Tabs2, "Computing")
s2_furnishing <- get_data(Shopper_Tabs2, "Home furnishings")
s2_in_store_factors <- get_data(Shopper_Tabs2, "FB_08a")
s2_online_factors <- get_data(Shopper_Tabs2, "FB_08b")

# This section generates the individual tables for shopper_tabs3
s3_gsa_summary_top2 <- get_data(Shopper_Tabs3, "Summary Top 2 Box")
s3_nbt_summary_hd_wc <- get_data(Shopper_Tabs3, "Have already done it and will likely continue")
s3_sms_general <- get_data(Shopper_Tabs3, "FBS_1 - Social Media Shopping")
s3_sms_why_not <- get_data(Shopper_Tabs3, "FBS_1a")
s3_sms_attitudes_top2 <- get_data(Shopper_Tabs3, "FBS_2 - Social Media Shopping.*Top 2 Box")
s3_sms_attitudes_bot2 <- get_data(Shopper_Tabs3, "FBS_2 - Social Media Shopping.*Bottom 2 Box")
s3_sms_attitudes_fun <- get_data(Shopper_Tabs3, "Shopping on social media networks is fun")
s3_sms_attitudes_uncomfortable <- get_data(Shopper_Tabs3, "I feel uncomfortable with the current amount of advertising I see on social media networks")
s3_sms_attitudes_targeted <- get_data(Shopper_Tabs3, "On my social media networks I get targeted with the best products for me")
s3_sms_attitudes_nfm <- get_data(Shopper_Tabs3, "Shopping on sicial media networks is not for someone like me")
s3_sms_attitudes_conveniences <- get_data(Shopper_Tabs3, "networks is convenient")
s3_nbt_summary_hd_wnc <- get_data(Shopper_Tabs3, "Have already done it and will not likely continue")
s3_nbt_summary_hn_wn <- get_data(Shopper_Tabs3, "Have not done it and will not")
s3_gsa_summary_bot2 <- get_data(Shopper_Tabs3, "Summary Bottom 2 Box")
```
*This gets the initial cleaned data for the shopper tab data and then generates the individual tibbles to be able to work with.

## view all data and generated data
```{r view_data}

# Initial data after being cleaned
#view(Shopper_Tabs1)
#view(Shopper_Tabs2)
#view(Shopper_Tabs3)

# Check first, mid, last of shopper_tabs1
#view(s1_past_six_months)
#view(s1_mobile_devices)
#view(s1_household_washing)
#view(s1_haircare)
#view(s1_skincare)
#view(s1_cosmetics)
#view(s1_packaged_food)
#view(s1_toys)
#view(s1_small_home_appliances)
#view(s1_fashion)
#view(s1_healthcare)
#view(s1_major_home_appliances)
#view(s1_replacement_auto)
#view(s1_streaming)
#view(s1_wearables)
#view(s1_computing)
#view(s1_home_furnishings)

# Check first, mid, last of shopper_tabs2
#view(s2_smartphones)
#view(s2_household_washing)
#view(s2_haircare)
#view(s2_skincare)
#view(s2_cosmetics)
#view(s2_packaged_food)
#view(s2_toys)
#view(s2_small_home_appliances)
#view(s2_fashion)
#view(s2_major_home_appliances)
#view(s2_replacement_auto)
#view(s2_streaming)
#view(s2_wearables)
#view(s2_computing)
#view(s2_furnishing)
#view(s2_in_store_factors)
#view(s2_online_factors)

# Check first, mid, last of shopper_tabs3
#view(s3_gsa_summary_top2)
#view(s3_nbt_summary_hd_wc)
#view(s3_sms_general)
#view(s3_sms_why_not)
#view(s3_sms_attitudes_top2)
#view(s3_sms_attitudes_bot2)
#view(s3_sms_attitudes_fun)
#view(s3_sms_attitudes_uncomfortable)
#view(s3_sms_attitudes_targeted)
#view(s3_sms_attitudes_nfm)
#view(s3_sms_attitudes_conveniences)
#view(s3_nbt_summary_hd_wnc)
#view(s3_nbt_summary_hn_wn)
#view(s3_gsa_summary_bot2)

```
*Create views for any/all initialized data in this Rmd file.




#Shopper_tabs1
```{r investigate_shopper_tabs1}

```

#Shopper_tabs2
```{r investigate_shopper_tabs2}

```

#Shopper_tabs3

## Visualization
```{r agree_bargraph}
agree_bargraph <- function(data, demo_colm, demo_amt, title) {
  #fileName <- "images/plot"
  #num <- 1
  #while(file.exists(paste(fileName, ".png"))) {
  #    fileName <- paste(fileName, num, sep="")
  #    num <- num + 1
  #}
  data %>%
    ggplot(aes(x=demo_colm, y=as.numeric(demo_amt), 
             fill = demo_colm, 
             color = demo_colm)) +
    facet_wrap(~question) +
    geom_bar(stat="identity", position=position_dodge()) +
    # define colors
    scale_fill_manual(values=1:7) +
    scale_color_manual(values=1:7) +
    # add text and define color
    geom_text(aes(label=demo_amt), vjust=1.6, color="white", 
            # define text position and size
            position = position_dodge(0.9),  size=3.5) +     
    theme_bw() +
    theme(axis.text.x=element_blank(), axis.title.x = element_blank(), legend.title = element_blank()) +
      ggtitle(title) + 
      labs(y='Number of surveyees')
    #ggsave(paste(fileName, ".png"))
}
```
* This function generates a plot. The commentted section is used for exporting a saving multiple plots. -

## Comparisons.
```{r fun comparison}
#### Fun comparison ####
# unweighted data
# s3_fun_unweighted <- get_weighted(s3_sms_attitudes_fun, 1) %>%
#   pivot_data(.) 
# agree_bargraph(s3_fun_unweighted, s3_fun_unweighted$Gender, s3_fun_unweighted$gender_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_unweighted, s3_fun_unweighted$ages, s3_fun_unweighted$ages_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_unweighted, s3_fun_unweighted$incomes, s3_fun_unweighted$incomes_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_unweighted, s3_fun_unweighted$education, s3_fun_unweighted$education_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_unweighted, s3_fun_unweighted$kids, s3_fun_unweighted$kids_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_unweighted, s3_fun_unweighted$employed, s3_fun_unweighted$employed_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_unweighted, s3_fun_unweighted$alcoholic, s3_fun_unweighted$alcoholic_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_unweighted, s3_fun_unweighted$ethnicity, s3_fun_unweighted$ethnicity_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_unweighted, s3_fun_unweighted$hispanic, s3_fun_unweighted$hispanic_amount, "Shopping on social media networks is fun.")
# # weighted data
# s3_fun_weighted <- get_weighted(s3_sms_attitudes_fun, 2) %>%
#     pivot_data(.)
# agree_bargraph(s3_fun_weighted, s3_fun_weighted$Gender, s3_fun_weighted$gender_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_weighted, s3_fun_weighted$ages, s3_fun_weighted$ages_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_weighted, s3_fun_weighted$incomes, s3_fun_weighted$incomes_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_weighted, s3_fun_weighted$education, s3_fun_weighted$education_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_weighted, s3_fun_weighted$kids, s3_fun_weighted$kids_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_weighted, s3_fun_weighted$employed, s3_fun_weighted$employed_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_weighted, s3_fun_weighted$alcoholic, s3_fun_weighted$alcoholic_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_weighted, s3_fun_weighted$ethnicity, s3_fun_weighted$ethnicity_amount, "Shopping on social media networks is fun.")
# agree_bargraph(s3_fun_weighted, s3_fun_weighted$hispanic, s3_fun_weighted$hispanic_amount, "Shopping on social media networks is fun.")
```
```{r uncomfy comparison}
#### Uncomfortable comparison ####
# unweighted data
# s3_uncomfy_unweighted <- get_weighted(s3_sms_attitudes_uncomfortable, 1) %>%
#     pivot_data(.)
# agree_bargraph(s3_uncomfy_unweighted, s3_uncomfy_unweighted$Gender, s3_uncomfy_unweighted$gender_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_unweighted, s3_uncomfy_unweighted$ages, s3_uncomfy_unweighted$ages_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_unweighted, s3_uncomfy_unweighted$incomes, s3_uncomfy_unweighted$incomes_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_unweighted, s3_uncomfy_unweighted$education, s3_uncomfy_unweighted$education_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_unweighted, s3_uncomfy_unweighted$kids, s3_uncomfy_unweighted$kids_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_unweighted, s3_uncomfy_unweighted$employed, s3_uncomfy_unweighted$employed_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_unweighted, s3_uncomfy_unweighted$alcoholic, s3_uncomfy_unweighted$alcoholic_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_unweighted, s3_uncomfy_unweighted$ethnicity, s3_uncomfy_unweighted$ethnicity_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_unweighted, s3_uncomfy_unweighted$hispanic, s3_uncomfy_unweighted$hispanic_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# # weighted data
# s3_uncomfy_weighted <- get_weighted(s3_sms_attitudes_uncomfortable, 2) %>%
#     pivot_data(.)
# agree_bargraph(s3_uncomfy_weighted, s3_uncomfy_weighted$Gender, s3_uncomfy_weighted$gender_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_weighted, s3_uncomfy_weighted$ages, s3_uncomfy_weighted$ages_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_weighted, s3_uncomfy_weighted$incomes, s3_uncomfy_weighted$incomes_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_weighted, s3_uncomfy_weighted$education, s3_uncomfy_weighted$education_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_weighted, s3_uncomfy_weighted$kids, s3_uncomfy_weighted$kids_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_weighted, s3_uncomfy_weighted$employed, s3_uncomfy_weighted$employed_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_weighted, s3_uncomfy_weighted$alcoholic, s3_uncomfy_weighted$alcoholic_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_weighted, s3_uncomfy_weighted$ethnicity, s3_uncomfy_weighted$ethnicity_amount, "Feels uncomfortable with the current amount of advertising on social media.")
# agree_bargraph(s3_uncomfy_weighted, s3_uncomfy_weighted$hispanic, s3_uncomfy_weighted$hispanic_amount, "Feels uncomfortable with the current amount of advertising on social media.")
```
```{r targeted comparison}
#### Targeted comparison ####
# unweighted data
# s3_targeted_unweighted <- get_weighted(s3_sms_attitudes_targeted, 1) %>%
#     pivot_data(.)
# agree_bargraph(s3_targeted_unweighted, s3_targeted_unweighted$Gender, s3_targeted_unweighted$gender_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_unweighted, s3_targeted_unweighted$ages, s3_targeted_unweighted$ages_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_unweighted, s3_targeted_unweighted$incomes, s3_targeted_unweighted$incomes_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_unweighted, s3_targeted_unweighted$education, s3_targeted_unweighted$education_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_unweighted, s3_targeted_unweighted$kids, s3_targeted_unweighted$kids_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_unweighted, s3_targeted_unweighted$employed, s3_targeted_unweighted$employed_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_unweighted, s3_targeted_unweighted$alcoholic, s3_targeted_unweighted$alcoholic_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_unweighted, s3_targeted_unweighted$ethnicity, s3_targeted_unweighted$ethnicity_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_unweighted, s3_targeted_unweighted$hispanic, s3_targeted_unweighted$hispanic_amount, "Get's targeted with the best products for them.")
# # weighted data
# s3_targeted_weighted <- get_weighted(s3_sms_attitudes_targeted, 2) %>%
#     pivot_data(.)
# agree_bargraph(s3_targeted_weighted, s3_targeted_weighted$Gender, s3_targeted_weighted$gender_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_weighted, s3_targeted_weighted$ages, s3_targeted_weighted$ages_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_weighted, s3_targeted_weighted$incomes, s3_targeted_weighted$incomes_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_weighted, s3_targeted_weighted$education, s3_targeted_weighted$education_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_weighted, s3_targeted_weighted$kids, s3_targeted_weighted$kids_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_weighted, s3_targeted_weighted$employed, s3_targeted_weighted$employed_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_weighted, s3_targeted_weighted$alcoholic, s3_targeted_weighted$alcoholic_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_weighted, s3_targeted_weighted$ethnicity, s3_targeted_weighted$ethnicity_amount, "Get's targeted with the best products for them.")
# agree_bargraph(s3_targeted_weighted, s3_targeted_weighted$hispanic, s3_targeted_weighted$hispanic_amount, "Get's targeted with the best products for them.")
```
```{r not for me comparison}
#### Not for me comparison ####
# unweighted data
# s3_nfm_unweighted <- get_weighted(s3_sms_attitudes_nfm, 1) %>%
#     pivot_data(.)
# agree_bargraph(s3_nfm_unweighted, s3_nfm_unweighted$Gender, s3_nfm_unweighted$gender_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_unweighted, s3_nfm_unweighted$ages, s3_nfm_unweighted$ages_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_unweighted, s3_nfm_unweighted$incomes, s3_nfm_unweighted$incomes_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_unweighted, s3_nfm_unweighted$education, s3_nfm_unweighted$education_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_unweighted, s3_nfm_unweighted$kids, s3_nfm_unweighted$kids_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_unweighted, s3_nfm_unweighted$employed, s3_nfm_unweighted$employed_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_unweighted, s3_nfm_unweighted$alcoholic, s3_nfm_unweighted$alcoholic_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_unweighted, s3_nfm_unweighted$ethnicity, s3_nfm_unweighted$ethnicity_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_unweighted, s3_nfm_unweighted$hispanic, s3_nfm_unweighted$hispanic_amount, "Shopping on social media is not for them.")
# # weighted data
# s3_nfm_weighted <- get_weighted(s3_sms_attitudes_nfm, 2) %>%
#     pivot_data(.)
# agree_bargraph(s3_nfm_weighted, s3_nfm_weighted$Gender, s3_nfm_weighted$gender_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_weighted, s3_nfm_weighted$ages, s3_nfm_weighted$ages_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_weighted, s3_nfm_weighted$incomes, s3_nfm_weighted$incomes_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_weighted, s3_nfm_weighted$education, s3_nfm_weighted$education_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_weighted, s3_nfm_weighted$kids, s3_nfm_weighted$kids_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_weighted, s3_nfm_weighted$employed, s3_nfm_weighted$employed_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_weighted, s3_nfm_weighted$alcoholic, s3_nfm_weighted$alcoholic_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_weighted, s3_nfm_weighted$ethnicity, s3_nfm_weighted$ethnicity_amount, "Shopping on social media is not for them.")
# agree_bargraph(s3_nfm_weighted, s3_nfm_weighted$hispanic, s3_nfm_weighted$hispanic_amount, "Shopping on social media is not for them.")
```
```{r convenient comparison}
#### conveneient comparison ####
# unweighted data
# s3_easy_unweighted <- get_weighted(s3_sms_attitudes_conveniences, 1) %>%
#     pivot_data(.)
# agree_bargraph(s3_easy_unweighted, s3_easy_unweighted$Gender, s3_easy_unweighted$gender_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_unweighted, s3_easy_unweighted$ages, s3_easy_unweighted$ages_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_unweighted, s3_easy_unweighted$incomes, s3_easy_unweighted$incomes_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_unweighted, s3_easy_unweighted$education, s3_easy_unweighted$education_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_unweighted, s3_easy_unweighted$kids, s3_easy_unweighted$kids_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_unweighted, s3_easy_unweighted$employed, s3_easy_unweighted$employed_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_unweighted, s3_easy_unweighted$alcoholic, s3_easy_unweighted$alcoholic_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_unweighted, s3_easy_unweighted$ethnicity, s3_easy_unweighted$ethnicity_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_unweighted, s3_easy_unweighted$hispanic, s3_easy_unweighted$hispanic_amount, "It's convenient and easy!")
# # weighted data
# s3_easy_weighted <- get_weighted(s3_sms_attitudes_conveniences, 2) %>%
#     pivot_data(.)
# agree_bargraph(s3_easy_weighted, s3_easy_weighted$Gender, s3_easy_weighted$gender_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_weighted, s3_easy_weighted$ages, s3_easy_weighted$ages_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_weighted, s3_easy_weighted$incomes, s3_easy_weighted$incomes_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_weighted, s3_easy_weighted$education, s3_easy_weighted$education_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_weighted, s3_easy_weighted$kids, s3_easy_weighted$kids_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_weighted, s3_easy_weighted$employed, s3_easy_weighted$employed_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_weighted, s3_easy_weighted$alcoholic, s3_easy_weighted$alcoholic_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_weighted, s3_easy_weighted$ethnicity, s3_easy_weighted$ethnicity_amount, "It's convenient and easy!")
# agree_bargraph(s3_easy_weighted, s3_easy_weighted$hispanic, s3_easy_weighted$hispanic_amount, "It's convenient and easy!")
```
